Combined annotation exploration for SCPCP000006

### 2025-03-17 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
fix a few more spots including remaining genes

| first level annotation | second level annotation | selection of the cells | marker genes for validation | CNV validation |
|----|----|----|----|----|
| normal | endothelial | `compartment == "endothelium" & predicted.score > pred.thr` | `VWF` | no CNV |
| normal | immune | `compartment == "immune" & predicted.score > pred.thr` | `PTPRC`, `CD163`, `CD68` | no CNV |
| normal | kidney | `compartment == "fetal_nephron" & predicted.score > pred.thr & cnv_score < cnv.thr.lower` | `CDH1`, `PODXL`, `LTL` | no CNV |
| normal | stroma | `compartment == "stroma" & predicted.score > pred.thr & cnv_score < cnv.thr.upper` | `VIM` | no CNV |
| cancer | stroma | `compartment == "stroma" & cnv_score > cnv.thr.upper` | `VIM` | `proportion_cnv_chr: 1, 4, 11, 16, 17, 18` |
| cancer | blastema | `compartment == "fetal_nephron" & cell_type == "mesenchymal cell" & cnv_score > cnv.thr.upper` | `CITED1` | `proportion_cnv_chr: 1, 4, 11, 16, 17, 18` |
| cancer | epithelial | `compartment == "fetal_nephron" & cell_type != "mesenchymal cell" & cnv_score > cnv.thr.upper` | `CDH1` | `proportion_cnv_chr: 1, 4, 11, 16, 17, 18` |
| unknown | \- | the rest of the cells | \- | \- |

@@

We simply checked the `cnv_chr` for each chromosome across cells.

@@

- validate that mostly tumor cells do present high percentages of cells with CNV (by definition)
- identify chromosome and cell types that might be more sensitive to *FALSE* positive CNV, such as `chr6p` which is a hub for immune genes
- get the repartition per sample of the CNV

@@

#### Immune, `PTPRC` expression

@@

#### Endothelium, `VWF` expression

@@

##### `COL6A3` expression

@@

##### `THY1` expression

@@

##### `CITED1` expression

@@

##### `NCAM1` expression

@@

##### `SIX2` expression

@@

##### `CDH1` expression

@@

##### `PODXL` expression

>>>>

| first level annotation | second level annotation | selection of the cells | marker genes for validation | CNV validation |
|----|----|----|----|----|
| normal | endothelial | `compartment == "endothelium" & predicted.score > pred.thr` | *VWF* | no CNV |
| normal | immune | `compartment == "immune" & predicted.score > pred.thr` | *PTPRC*, *CD163*, *CD68* | no CNV |
| normal | kidney | `compartment == "fetal_nephron" & predicted.score > pred.thr & cnv_score < cnv.thr.lower` | *CDH1*, *PODXL*, *LTL* | no CNV |
| normal | stroma | `compartment == "stroma" & predicted.score > pred.thr & cnv_score < cnv.thr.upper` | *VIM* | no CNV |
| cancer | stroma | `compartment == "stroma" & cnv_score > cnv.thr.upper` | *VIM* | `proportion_cnv_chr: 1, 4, 11, 16, 17, 18` |
| cancer | blastema | `compartment == "fetal_nephron" & cell_type == "mesenchymal cell" & cnv_score > cnv.thr.upper` | *CITED1* | `proportion_cnv_chr: 1, 4, 11, 16, 17, 18` |
| cancer | epithelial | `compartment == "fetal_nephron" & cell_type != "mesenchymal cell" & cnv_score > cnv.thr.upper` | *CDH1* | `proportion_cnv_chr: 1, 4, 11, 16, 17, 18` |
| unknown | \- | the rest of the cells | \- | \- |

@@

For each cell, we checked the level of CNV for each chromosome.

@@

- validate that mostly tumor cells do present high percentages of cells with CNV (by definition)
- identify chromosome and cell types that might be more sensitive to *FALSE* positive CNV, such as *chr6p* which is a hub for immune genes
- get the repartition per sample of the CNV

@@

#### Immune, *PTPRC* expression

@@

#### Endothelium, *VWF* expression

@@

##### *COL6A3* expression

@@

##### **THY1* expression

@@

##### *CITED1* expression

@@

##### *NCAM1* expression

@@

##### *SIX2* expression

@@

##### *CDH1* expression

@@

##### *PODXL* expression
